---
title: "Lab 00 - Hello IDS!"
author: "Carla Martin"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ash Warnes", "Kumi Stevens", "Selena Bobbica", 
           "Shreya"),
  github_username = c("ashburyw7", "kumi-stevens", "selena-314", 
                      "ggshreya"), 
  colour = c("green4", "goldenrod1", "pink", 
             "blue4"),
  hobby = c("art", "climbing", "violin", 
            "cello"),
  favourite_number = c(7, 3, 7, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


graph shows github username against their favourite number, and the bar is the persons favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "introductions")
```

labs adds labels to the axis and a title to the diagram

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

make people select options from a list since if people type technically similar hobbies in a different way they will be shown as different things. you could also present it as a pie chart instead.
